Women highest Level Education in 20 years

### 2023-03-12 outputs/paper/paper.qmd
Script Writing, csv reading in quarto

library(tidyverse)
library(palmerpenguins)
```

>>>>

#### Initialize quarto workspace by reading csv's ####
library(tidyverse)
library(here)

gss2000_cleaned <- read.csv(here::here("outputs/data/gss2000_cleaned.csv"))
gss2002_cleaned <- read.csv(here::here("outputs/data/gss2002_cleaned.csv"))
gss2004_cleaned <- read.csv(here::here("outputs/data/gss2004_cleaned.csv"))
gss2006_cleaned <- read.csv(here::here("outputs/data/gss2006_cleaned.csv"))
gss2008_cleaned <- read.csv(here::here("outputs/data/gss2008_cleaned.csv"))
gss2010_cleaned <- read.csv(here::here("outputs/data/gss2010_cleaned.csv"))
gss2012_cleaned <- read.csv(here::here("outputs/data/gss2012_cleaned.csv"))
gss2014_cleaned <- read.csv(here::here("outputs/data/gss2014_cleaned.csv"))
gss2016_cleaned <- read.csv(here::here("outputs/data/gss2016_cleaned.csv"))
gss2018_cleaned <- read.csv(here::here("outputs/data/gss2018_cleaned.csv"))
gss2021_cleaned <- read.csv(here::here("outputs/data/gss2021_cleaned.csv"))

```
